fsOGTT Pre- and Post-ETI

### 2025-07-23 Christine Chan/EnVision CF/fsOGTT_pre_post_ETI.qmd
both study IDs for EnVision and GEM fsOGTT

@@

    study_id, Date, age_visit, sex, origin_race, ethnicity, CFTR,

@@

df$pancreatic_status <- factor(df$pancreatic_status, levels = 1:2)

@@

  mutate(ETI = 0, pre_post = "Pre") %>%

@@

    subject_id, date_of_visit, age_at_visit_1, gender, race_ethnicity,
    cf_genotype, cf_pancreatic, ETI, pre_post, average_bmi, fev1_percent,
    group_category, lab_ogtt_fasting, min_10_glucose, min_30_glucose,
    lab_ogtt_1_hour_glucose, min_90_glucose, lab_ogtt_2_hour_glucose,
    min_150_glucose, min_180_glucose, min_0_insulin, min_10_insulin,
    min_30_insulin, min_60_insulin, min_90_insulin, min_120_insulin,
    min_150_insulin, min_180_insulin, min_0_c_peptide, min_10_c_peptide,
    min_30_c_peptide, min_60_c_peptide, min_90_c_peptide, min_120_c_peptide,
    min_150_c_peptide, min_180_c_peptide

@@

    study_id = subject_id, Date = date_of_visit, age_visit = age_at_visit_1,

@@

gem$pancreatic_status <- factor(gem$pancreatic_status, levels = 1:2)

@@

@@

gem <- gem %>% filter(study_id %in% ids$`GEM ID`)
# Convert to EnVision IDs
gem$study_id <- ids$`EnVision ID`[match(gem$study_id, ids$`GEM ID`)]
# Merge, keep only pre/post
df <- full_join(df, gem) %>% filter(!is.na(pre_post))

@@

>>>>

  mutate(gem_id = NA, study = "EnVision CF") %>%

@@

    study_id, gem_id, study, Date, age_visit, sex, origin_race, ethnicity, CFTR,

@@

df$pancreatic_status <- factor(df$pancreatic_status,
  levels = 1:2,
  labels = c("Sufficient", "Insufficient")

@@

  mutate(ETI = 0, pre_post = "Pre", study_id = NA, study = "GEM-CF") %>%

@@

    study_id, subject_id, study, date_of_visit, age_at_visit_1, gender,
    race_ethnicity, cf_genotype, cf_pancreatic, ETI, pre_post, average_bmi,
    fev1_percent, group_category, lab_ogtt_fasting, min_10_glucose,
    min_30_glucose, lab_ogtt_1_hour_glucose, min_90_glucose,
    lab_ogtt_2_hour_glucose, min_150_glucose, min_180_glucose,
    min_0_insulin, min_10_insulin, min_30_insulin, min_60_insulin,
    min_90_insulin, min_120_insulin, min_150_insulin, min_180_insulin,
    min_0_c_peptide, min_10_c_peptide, min_30_c_peptide, min_60_c_peptide,
    min_90_c_peptide, min_120_c_peptide, min_150_c_peptide, min_180_c_peptide

@@

    gem_id = subject_id, Date = date_of_visit, age_visit = age_at_visit_1,

@@

gem$pancreatic_status <- factor(gem$pancreatic_status,
  levels = 1:2,
  labels = c("Sufficient", "Insufficient")

@@

# IDs
gem$study_id <- ids$`EnVision ID`[match(gem$gem_id, ids$`GEM ID`)]
df$gem_id <- ids$`GEM ID`[match(df$study_id, ids$`EnVision ID`)]

@@

gem <- gem %>% filter(gem_id %in% ids$`GEM ID`)
# Merge, keep only pre/post, sort by ID and date
df <- rbind(df, gem) %>% filter(!is.na(pre_post))

@@

df <- df %>% arrange(study_id, Date)
